### 2016-06-28 publications/Journal/5-related-work.tex
Re-add publication folder + draft journal paper.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>
Updated related work.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

While PythonPDEVS offers very fast turnaround cycles, due to the use of an interpreted language, simulation performance was easily outdone by compiled simulation kernels.
In terms of performance, adevs~\cite{adevs} offered much faster simulation, at the cost of a significant compilation time.
The turnaround cycle in adevs is much slower though, specifically because the complete simulation kernel is implemented using templates in header files.
As a result, the complete simulation kernel has to be compiled again every time.
Dxex compromises, as vle~\cite{vle} or PowerDEVS~\cite{PowerDEVS}, by separating the simulation kernel into a shared library.
After the initial compilation of the simulation tool, only the model has to be compiled and linked to the library.
This significantly shortens the turnaround cycle, while still offering good performance.
In terms of performance, dxex is shown to be competitive with adevs.
While a more extensive set of benchmarks is required to make accurate comparisons, initial results are promising.
Despite its high performance, adevs does not support optimistic synchronization, which we have shown to be highly relevant.

@@

>>>>

While PythonPDEVS offers very fast turnaround cycles, due to the use of an interpreted language, simulation performance was easily outdone by compiled simulation kernels.
In terms of performance, adevs~\cite{adevs} offered much faster simulation, at the cost of a significant compilation time.
The turnaround cycle in adevs is much slower though, specifically because the complete simulation kernel is implemented using templates in header files.
As a result, the complete simulation kernel has to be compiled again every time.
Dxex compromises, as vle~\cite{vle} or PowerDEVS~\cite{PowerDEVS}, by separating the simulation kernel into a shared library.
After the initial compilation of the simulation tool, only the model has to be compiled and linked to the library.
This significantly shortens the turnaround cycle, while still offering good performance.
In terms of performance, dxex is shown to be competitive with adevs.
Despite its high performance, adevs does not support optimistic synchronization, which we have shown to be highly relevant.

@@

% Paragraph runtime switching
In the PDES community the problem of choosing between synchronization protocols is well known and documented \cite{Jha:1994:UFC:195291.182480}.
In the work of \cite{Das:1996:APP:256562.256602} the challenges facing the implementation of runtime switching between protocols is explored.
A PDES implementation of such a feature was presented in \cite{perumalla2005musik}. 
Our contribution entails bringing this feature to the PDEVS community.

% Paragraph allocation effects
Our emphasis on model allocation as a key factor in parallel performance has been studied in detail by the PDES community \cite{PDESpartitioning}. 
Referenced as partitioning of the simulation model, most studies distinguish between communication overhead and computational distribution (load balancing) as the two dimensions to partition over.
Partitioning a simulation model is identified as an issue in the work of \cite{Scalability} to achieve scalability. 
In \cite{PDEVSpartitioning} partitioning is studied in a PDEVS context with attention to load balancing and communication overhead.
Our contribution studies the effect of partitioning with emphasis on the effect of communication between processes and in the presence of a flattened hierarchy. 
We focus on static partitioning since this is a limiting factor for our conservative synchronization implementation which does not support model relocation.
